```{r, echo=FALSE, include=FALSE}
## Get VERSION and create file names
ver <- sub(x=grep(x=readLines("DESCRIPTION"), pattern="^Version: ",
                  value=TRUE),
           pattern="^Version: ", replacement="")
pkg.name <- "legtheme_"
pkg.source <- paste0(pkg.name, ver, ".tar.gz")
pkg.win <- paste0(pkg.name, ver, ".zip")
```

# tcctemplate `r ver`

<!-- [![Build Status](https://travis-ci.org/leg-ufpr/legtheme.svg?branch=master)](https://travis-ci.org/leg-ufpr/legtheme) -->

DEST UFPR template for documents.

## Usage

<!-- After installing (sse below), you can create a draft document from one -->
<!-- of the themes available: -->

<!-- - `beamer_leg` is a theme for beamer slides -->
<!-- - `proj_generico` is a theme for a generic project or any other similar -->
<!--   document in PDF -->

To create a draft for use:

```{r, eval=FALSE}
library(rmarkdown)
draft(file = "projeto.Rmd", template = "projeto_template",
      package = "tcctemplate", create_dir = FALSE, edit = FALSE)
```
This will create (in the current directory) a file named `proj.Rmd`
which can be further rendered with

```{r, eval=FALSE}
render("proj.Rmd")
```

<!-- Similarly, to create a draft document for the `proj_generico` theme, -->
<!-- just use: -->

```{r, eval=FALSE, include=FALSE}
draft(file = "proj.Rmd", template = "proj_generico",
      package = "legtheme", create_dir = FALSE, edit = FALSE)
render("proj.Rmd")
```

## Download and install

The easiest way to install is directly from this repository with the
**remotes** (or **devtools**) packages

```{r, eval=FALSE}
remotes::install_github("fernandomayer/tcctemplate")
```

## Authors

- [Fernando de Pol Mayer][]

## License

MIT. See [LICENSE](./LICENSE)

<!-- links -->


[Fernando de Pol Mayer]: http://www.leg.ufpr.br/~fernandomayer
